 ---
title: "Social Protection Project"
subtitle: "Field Data Analysis — Group Project"
author:
  - name: "Carina"
  - name: "Liyuansheng"
  - name: "Natalia"
  - name: "Farhan"
date: today
format: pdf
editor: visual
project:
  execute-dir: project
---

## Introduction

In order for Field Data Analysis our group will analyze which social protection program is the most associate with the reducing poverty gap between Unconditional Cash Transfer and Conditional Cash Transfer.

### Theoretical Framework

### Reaserch Objective and Research Question

## Data Sources

We use data provided by ASPIRE World Bank

## Step by step

### Library and Dataset

You can add options to executable code like this

```{r}
#install.packages("here")
install.packages("readxl")
library(here)
library(tidyverse)
library(readxl)

here()

df <- read.csv(here("data/PER-Table1-Key-Indicators.csv"))

# Check available sheets before loading
excel_sheets(here("data/PER-Table7-Coverage12-Programs.xlsx"))
```

```{r}
df_coverage <- read_excel(here("data/PER-Table7-Coverage12-Programs.xlsx"))

# Peek at structure to identify relevant columns
glimpse(df_coverage)
```

```{r}
# Filter for UCT and CCT programs
df_uct_cct <- df_coverage |>
  filter(str_detect(program_type, regex("unconditional|conditional cash", ignore_case = TRUE)))

head(df_uct_cct)
```

### Cleaning dataset

### Descriptive Data

### Visualization

### Modeling

## Conclusion

## Ethics Disclosure

## Reference
